\begin{thebibliography}{9}
\label{sec:ref}
\addcontentsline{toc}{section}{\nameref{sec:ref}}

% Reference to casing cad software missing
\bibitem{cad}
https://www.autodesk.com/products/fusion-360/overview
\bibitem{wind_meas}
	\url{ltu.diva-portal.org/smash/get/diva2:1039147/FULLTEXT01.pdf}
\bibitem{bqStudio}
Battery Management Studio (bqStudio) offers a full suite of robust tools to assist with the process of evaluating, designing with, configuring, testing, or otherwise utilizing TI Battery management products. \url{http://www.ti.com/tool/bqstudio}
\bibitem{stm32cubemx}
  \url{http://www.st.com/en/development-tools/stm32cubemx.html}
\bibitem{kicad}
  KiCad open source electronics design,
  \url{kicad-pcb.org/}
\bibitem{overprotection}
	Overvoltage and Reverce-voltage Protection in Automotive Systems,
	Application note 760, \emph{Maxim integrated}, Apr 02, 2002, 
	\url{https://www.maximintegrated.com/en/app-notes/index.mvp/id/760}
\bibitem{x-cube-ble1}
  \url{http://www.st.com/en/embedded-software/x-cube-ble1.html}
\bibitem{x-cube-mems1}
  \url{http://www.st.com/en/embedded-software/x-cube-mems1.html}
\bibitem{bluenrg-app}
  \url{http://play.google.com/store/apps/details?id=com.st.blunrg}
\bibitem{x-nucleo-idb05a1}
  \url{http://www.st.com/en/ecosystems/x-nucleo-idb05a1.html}
\bibitem{x-nucleo-iks01a2}
  \url{http://www.st.com/en/ecosystems/x-nucleo-iks01a2.html}
\bibitem{madgwick}
  \url{http://x-io.co.uk/open-source-imu-and-ahrs-algorithms}
\bibitem{madgwick-report}
  \url{http://x-io.co.uk/res/doc/madgwick_internal_report.pdf}
\bibitem{gps}
  \url{http://update.maestro-wireless.com/GNSS/A2235-H/Maestro_GPS_Evaluation_Kit_EVA2235_H_User_Manual_V01.pdf}
\bibitem{libnmea}
  \url{http://github.com/jacketizer/libnmea}
\bibitem{x-cube-53l0a}
  \url{http://www.st.com/content/st_com/en/products/ecosystems/stm32-open-development-environment/stm32-nucleo-expansion-boards/stm32-ode-sense-hw/x-nucleo-53l0a1.html}
\bibitem{android-service}
  \url{https://developer.android.com/reference/android/app/Service.html}
\bibitem{lat-long-calc}
  \url{https://www.movable-type.co.uk/scripts/latlong.html}
\bibitem{lm1117}
	KiCad library entry for voltage regulator component lm1117 by \emph{ObKo}, 2012  
  \url{https://github.com/ObKo/kicad-libraries/blob/master/libraries/lm1117.lib}
\bibitem{llc}
	Bi-directional Logic Level Converter, \emph{Sparkfun}, Aug 4, 1997,
	\url{https://cdn.sparkfun.com/tutorialimages/BD-LogicLevelConverter/an97055.pdf}
\bibitem{ftdi}
	KiCad library entry for USBtoSerial component FT232RL by \emph{jbaker0428}, Oct 3, 2010
	\url{https://github.com/jbaker0428/Kicad-Libraries/blob/master/library/ftdi.lib}
\bibitem{rhumb-line}
  \url{https://en.wikipedia.org/wiki/Rhumb_line}
\bibitem{equirectangular}
  \url{https://en.wikipedia.org/wiki/Equirectangular_projection}
\bibitem{haversine}
  \url{https://en.wikipedia.org/wiki/Haversine_formula}
\bibitem{sailing}
  \url{https://en.wikipedia.org/wiki/Sailing}
\bibitem{sail-force}
  \url{http://newt.phys.unsw.edu.au/~jw/sailing.html}
\bibitem{volvo}
  \url{https://sv.wikipedia.org/wiki/Volvo_Amazon}
\bibitem{png}
  \url{https://sv.wikipedia.org/wiki/PNG}
\bibitem{activity}
  \url{https://developer.android.com/reference/android/app/Activity.html}
\bibitem{uml}
  \url{https://en.wikipedia.org/wiki/Unified_Modeling_Language}
\bibitem{gl}
  \url{https://developer.android.com/reference/android/opengl/GLSurfaceView.html}
\bibitem{texttospeech}
  \url{https://developer.android.com/reference/android/speech/tts/TextToSpeech.html}
\bibitem{utter}
  \url{https://developer.android.com/reference/android/speech/tts/UtteranceProgressListener.html}
\bibitem{gmaps}
  \url{https://developers.google.com/maps/}
\bibitem{Tof_cover}
	\gls{st}, Spplication note: AN4907, \emph{VL53L0X ranging module cover window guidelines},
	\url{http://www.st.com/content/ccc/resource/technical/document/application_note/group0/9d/93/be/33/13/be/46/19/DM00326504/files/DM00326504.pdf/jcr:content/translations/en.DM00326504.pdf}
\bibitem{animal} 
D.L. Hall and J. Llinas. An introduction to multisensor data fusion. 
\textit{Proceedings of the}. IEEE, 85(1):6 –23, jan 1997

\bibitem{boken} 
B.R. Grover H. Patrick. Introduction to random signals and applied Kalman filtering. 1997
\textit{BOKEN}. 

\bibitem{SNAME} 
Society of Naval Architects and Marine Engineers (SNAME), "Principles of Naval Architecture", 1989, Vol. III,
\textit{SNAME}. 

 
\bibitem{nonlinear} 
Dr. Oliver Nelles
\\\texttt{nonlinear system identification.}

\bibitem{kf eff}
Duygun, M., Kutlu, L. \& Sickles, R.C. J Prod Anal (2016) 46: 155. \url{https://doi.org/10.1007/s11123-016-0477-z}
\bibitem{non-linear}
Noureldin ., Karamat T.B., Georgy J. (2013)\texttt{ Basic Navigational Mathematics, Reference Frames and the Earth’s Geometry. In: Fundamentals of Inertial Navigation, Satellite-based Positioning and their Integration.} Springer, Berlin, Heidelberg
\bibitem{cccv}
	Power Guy, \emph{Constant Current Constant voltage}, May 26, 2016, San Diego, USA,
  \url{https://www.us.tdk-lambda.com/media/292143/tdk-lambda-blog-052616.pdf}
\bibitem{UoC}
	\url{https://edg.uchicago.edu/tutorials/load_cell/}
\bibitem{load_cell}
	\url{http://www.te.com/commerce/DocumentDelivery/DDEController?Action=srchrtrv&DocNm=FX19&DocType=DS&DocLang=English}
\bibitem{animal}
D.L. Hall and J. Llinas. An introduction to multisensor data fusion. 
\textit{Proceedings of
the}. IEEE, 85(1):6 –23, jan 1997

\bibitem{signal_process}
Probability and Random Processes with Applications to Signal Processing, 4/E (2012). 
Henry Stark, John W Woods. Pearson Higher Education. 

\bibitem{Discrete_kalman}
	Donald E. Catlin, \emph{Estimation, Control, and the Discrete Kalman Filter}, 1989
\bibitem{pertubation}
  \url{https://en.wikipedia.org/wiki/Perturbation_theory}

\bibitem{book}%[p.26-27]
Weicker, P. (2014). \emph{A Systems Approach to Lithium-ion Battery Management}, Boston, Artech House. 

%\bibitem{book}[p.111]
%Weicker, P. (2014). A Systems Approach to Lithium-ion Battery Management. (pp.111). Boston: Artech House. 

%\bibitem{book}[p.111-112]
%Weicker, P. (2014). A Systems Approach to Lithium-ion Battery Management. (pp.111-112). Boston: Artech House.

%\bibitem{book}[p.183-185]
%Weicker, P. (2014). A Systems Approach to Lithium-ion Battery Management. (pp.183-185). Boston: Artech House.

%\bibitem{book}[p.35-38]
%Weicker, P. (2014). A Systems Approach to Lithium-ion Battery Management. (pp.35-38). Boston: Artech House.

\bibitem{webpage}
  \url{http://www.lygte-info.dk/info/battery%20protection%20UK.html}
(pp. [Page number starts]-[ends]).

\end{thebibliography}
